|

### 2025-02-18 docs/paper.qmd
new paper version

---
title: |
  | How does the Accounting Research Community
  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin while Jacqueline Klug and Victor van Pelt are affiliated with WHU Otto Beisheim School of Management. We thank Kris Hardies, Maximilian Müller as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, and WHU for providing helpful feedback. Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This work was supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes

editor: visual

@@

sd <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)
byu <- read_csv("../data/external/byu_author_data_anon.csv", show_col_types = FALSE)

@@

@@

gt_add_header_mpage_table <- function(x) {
  x <- sub("\\\\midrule", "\\\\midrule \\\\endhead", x)
  x
}

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
To understand how the accounting research community thinks about open science, we survey a sample of scholars who have published in leading accounting journals. Building on a voluntary disclosure-themed discussion of the costs and benefits of open accounting research, we document that accounting researchers tend to be more skeptical about the reproducibility of their influential findings than researchers from other social science areas are about theirs. Also, they are less familiar with the public sharing of research materials and pre-register their study designs less often. While they believe that accounting researchers in general and editors in particular favor research material sharing, they are skeptical about its actual prevalence in the accounting research community. We contrast these survey results with observational data, documenting that research material sharing is indeed relatively rare and often linked to journals with data and code sharing policies. We interpret this descriptive evidence as indicating an "accounting open science dilemma" and suggest strategies for addressing it.
\end{abstract}
```
```{=tex}
\vspace{0.5cm}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Research Material Sharing, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc}  \newline
\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc} \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```
\pagebreak

\setcounter{page}{1}

@@

Cumulative science builds on the reproducibility of research, which is the ability to recreate the results of prior studies using the same materials as those used by the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2020; @G_2023; @S_2023; @CGL_2024], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods. Open science implies conducting research in ways that allow others to collaborate and contribute. Two central open science methods that have been put forward as strategies to improve the reproducibility of our work are the public sharing of research materials and the pre-registration of study plans. Over the last years, there has been a significant uptake of these open sciences methods in social science areas outside of accounting [@FLCPSWMBP_2023].

Research material sharing and pre-registrations can be understood as disclosure mechanisms that allow researchers to contribute public goods to the research community while also signaling the quality of their work. However, limited individual benefits and significant direct as well as indirect costs make it likely that researchers, on average, will rationally under-engage in these activities, potentially resulting in a socially sub-optimal under-provision of public research materials and on overall lacking research transparency. Following these thoughts and building on prior literature in neighboring fields, we conduct a survey among accounting researchers to explore the perceptions and attitudes towards open science in our field.

Based on the responses of `r nrow(sd)` published accounting researchers, we find that attitudes toward open science clearly differ from those of other social science researchers. Most prominently, accounting researchers tend to hold a generally more pessimistic view of the reproducibility of influential work within their field. Compared to economists and sociologists, for example, accounting researchers are about half a point more skeptical on a 5-point Likert scale. Exploring this assessment across the respondents' demographics, we find this skepticism to be relatively stable. Analytical and qualitative researchers are somewhat more pessimistic. Analytical researchers tend to be particularly more critical of research that uses non-analytical methods.

Given this finding, one would expect accounting researchers to take a proactive stance and embrace two prominent open science methods that are expected to increase the reproducibility of research: The public sharing of research materials (i.e., data, code and research procedures) and the pre-registration of research plans. Turning first to the public sharing of research materials, we document that, again, compared to researchers from other social science areas, accounting researchers are somewhat less familiar with this activity and assess it to be somewhat less important. Familiarity is largest for respondents using archival, field, and experimental methods and lowest for respondents using qualitative methods, who also perceive the sharing of research materials as less important.

Similar to, albeit even more pronounced than, other social science researchers, there is a stark contrast in accounting researchers' perceived (prescriptive) importance of research material sharing, their stated willingness to share research materials, and their (descriptive) perception about actual sharing behavior in the accounting research community. 57% of our respondents state that they, at least sometimes, publicly share their research materials. In addition, our respondents believe that about 44% of them favor publicly sharing research materials, and they believe 61% of the top-six accounting editors to be in favor of publicly sharing research materials. Although this sounds comforting and consistent with a generally supportive stance of the accounting community toward research material sharing, the percentage comes down to a much more sobering 28% when respondents are asked about actual sharing behavior in the accounting research community. This assessment and the gap it reveals differ significantly across methodological areas. Analytical researchers have the most narrow gap (they expect 43% of accounting researchers to be in favor and 38% to actually share research materials). Archival researchers, in turn, have the widest gap (45% expected to be in favor versus 24% expected to actually share). The overall lowest numbers are again reported by qualitative researchers (36% versus 18%).

Regarding pre-registration, accounting researchers seem as familiar with the concept as other social science researchers. However, our respondents report that they started using it later than other social science researchers (roughly two years) and that they use it less frequently (17% versus 27%). Their trust in pre-registered work is generally comparable with other social science researchers but significantly lower than the trust levels of researchers in Psychology (the field that reports the highest usage rate of pre-registration). A detailed look into differences across methodological fields also reflects this, as we find that experimental researchers use pre-registration most (28%) and express the strongest belief that it increases the trustworthiness of research.

To contrast these perceptions from our survey with actual behavior, we gather additional observational data from a country-stratified random sample of `r nrow(authors)` authors of our target population. We find evidence for at least some form of research material sharing for 39% of the authors in this sample. This number is similar to the self-reported perception of actual research material sharing in our survey (i.e., 38%). However, when we further inspect the observational data, we find that research material sharing in accounting is largely an occasional compliance activity. For instance, for 7.5% of the papers written by the authors in the observational data show evidence for research material sharing. Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%. Furthermore, we document very few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.

In light of these numbers, a logical next step is to explore the main rationales for and against sharing research materials. We do so based on a short experimental design using a hypothetical scenario and by using our survey data.[^2] In our hypothetical scenario involving a fellow researcher requesting access to participants' research materials, our participants state that they would be very likely to share on average (mean probability is 72%). We find no evidence that this probability is affected by the randomized nature of the provided rationale (i.e., collaboration or control) and the provided scope of the sharing decision (public versus private sharing). Based on the verbal responses of our participants, researchers tend to share their materials as they believe that this improves the quality of their research and of research in general. Also, they share because they want to support their fellow researchers. The most commonly stated reasons for not sharing research materials are the proprietary nature of the data used (56% of respondents give this reason), the time it takes to make materials available (30%), and the fear of being scooped when materials become publicly available (23%). The reasons differ across methods. For qualitative researchers, deidentification problems are very prominent (46%), and analytical researchers consider the time it takes to make materials available far less of a reason than researchers using other methods (i.e., 9.5% versus 30% overall).

Collectively, our evidence speaks to the ongoing debate about reproducibility and openness of accounting research. We extend the survey evidence by @HLL_2020 by providing more detailed and current insights on the perceived benefits and costs of open science methods and by benchmarking the attitudes of the fields with neighboring disciplines. Also, we collaborate recent evidence on the robustness of empirical accounting [@G_2023; @S_2023; @LSA_2024; @CGL_2024] and management science [@FGHKO_2023] work by exploring some of the underlying reasons why our discipline might (or might not) have a reproducibility issue.

Our findings indicate somewhat of an "accounting open science dilemma": We accounting researchers tend to be skeptical about both the reproducibility of our work and the ability of research material sharing and pre-registration to improve it. This is consistent with these tools currently being less established in the accounting domain than in other fields. The challenges that hinder reproducibility and the potential effectiveness of open science methods vary across methodological paradigms. Qualitative research faces challenges different from archival quantitative work, and they both differ again from experimental studies. We conclude by discussing these challenges and providing suggestions on how our diagnosed dilemma might be overcome.

@@

Accounting is a field within the social sciences. As such, many of the arguments that have been developed with regard to the costs and benefits of open science in general [@MS_2019; @AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023] also apply to the field of accounting. In the following, we present and extend some of these thoughts in a voluntary disclosure framework [@LT_2005; @MS_2019; @BCLW_2010]. For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration. Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good. To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and, most likely, also the quality of research. Even if they are not really reusable or reusing them would be prohibitively costly, they still reduce the costs of reproducing the original work, thereby reducing assurance costs. As the work in auditing [e.g., @S_1980] posits, reduced auditing costs (easier reproduction) should lead to an overall increase in audit quality (more and better reproductions), resulting in better financial reporting quality (better research).

This means that, similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large. While intrinsic motivation for good research can be expected to be a strong determinant of individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public. So, are there any private benefits to sharing research materials? Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output. First, it increases the likelihood that mistakes, conditionally on being present, are being detected. As it seems safe to assume that such incidents impose a cost on sharing researchers, this should increase their incentives to increase research quality prior to sharing. Second, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study. Finally, uncovered mistakes are an important learning opportunity, likely improving research quality in the long run.

Based on these arguments, there are reasons to believe that voluntary research material sharing can act as a signal for research quality, creating an incentive for researchers to use it to signal the quality of their work in the publishing and career process. In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981]. One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the contemporary disclosure literature. Thus, for research materials sharing to be viable, it is important that the costs of sharing are sufficiently low, especially for researchers that produce high-quality work. Thus, it critically hinges on the above quality assurance process. Also, it depends on the direct and indirect costs of research material sharing to be bearable and at least comparable for high- and low-quality researchers.

The direct costs of research material sharing can be sizable. Preparing data, code and research procedures for dissemination requires time. While this time can also be expected to have a quality improvement effect (see above), at least some of the documentation work and code refactoring to increase accessibility and reusability creates costs that will not directly pay off on the quality of the underlying work. Another important factor to consider is the cost of maintaining publicly available materials. While some replication packages or similar materials are static in nature and require only limited maintenance, data and code packages can require ongoing updating and support activities. One important aspect of maintenance costs is that they increase significantly with public demand. As demand is directly linked to the scientific impact of the underlying work it can be argued that high maintenance cost sharing activities are likely to also be high benefit activities.

The indirect costs of research material sharing are first and foremost linked to the quality assurance process outlined above. Flaws in publicly shared research materials can trigger more behavioral effects (shame, regret) but also reputation costs. Another important aspect are proprietary costs from scientific competition. While likely to be positive from the societal perspective, the indirect individual costs of being "scooped" for an interesting follow-up project can be sizable. Finally, there is also the possibility of unethical misuse of shared research materials. Malevolent researchers might use shared materials without proper attribution or use it with a strategy of "reverse p-hacking", meaning creating reproductions or replications that communicate a biased picture of the overall evidence to increase their chances for publication.

Rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs. Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds. In a credence good market like research, signaling is a key mechanism to avoid market failure. Based on the discussion above, a critical aspect could be the proprietary cost of competition, as one could argue that this cost is higher for high quality researchers with innovative ideas than for low-quality researchers who will likely face limited demand for their materials. Also the risks of reputation costs or misuse of materials could be higher for high-quality researchers. On the other hand, it can be argued that direct costs should be lower for high-quality researchers because of superior skills. Finally, outside options should be generally higher for high-quality researchers, meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their materials private.

The discussion should sound somewhat familiar to those who study voluntary disclosures by firms. What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs. Instead, they are employed by academic institutions or act as civil servants. This can, to some extent, mute the relevance of the benefits and the costs outlined above, at least for researchers with tenured positions. In addition, the employing institutions might also interact with the decision of whether or not to make research materials available. They are designing performance and tenure evaluation criteria that incentivize researchers. Also, they compensate researchers for their time and they provide them with infrastructure that influences and at times drastically reduces the direct costs of research material sharing. They might even hold property rights on the intellectual capital that their employees generate. Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing. However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they value individual research achievements in form of publications and only rarely publicly available research materials.

Finally, publishers and journals are influential in research material sharing decisions as well. Leading journals have established demanding data and code sharing guidelines, essentially transforming the voluntary disclosure decision into a mandatory disclosure requirement. While journals also compete for the best papers and it is interesting to question how this competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.

@@

The first two questions are descriptive in nature. Assuming that the signaling mechanism above or other incentives have not succeeded in removing all insecurity about the reproducibility of influential accounting work, we expect to find some variation in our response with regard to research question one. More importantly, we want to compare the response of our sample with responses by researchers from other social science fields. The second question explores whether accounting researchers believe that research material sharing and pre-registration are viable strategies to increase the reproducibility of research. Again, comparing the views of accounting academics with the views of neighboring fields will be instrumental here.

The third question strives to understand the potential causes behind these assessments. Using a small experimental component, our survey tests whether two aspects of a hypothetical sharing request, its rationale (collaboration or control) and its scope (public versus private), affect the stated hypothetical likelihood of sharing. Our motivation for the treatments is that the rationale should shift the focus from benefits (collaboration) to costs (control) while the scope treatment should manipulate the salience of indirect costs. Besides studying the effect of these two experimental treatments, we also use verbal and structured survey response data to uncover perceived benefits and costs from research material sharing.

@@

Figure 4 graphically presents these findings, showing the frequencies along horizontal axes and centering them to a neutral midpoint. Only 39.6% of the accounting researchers deem research material sharing "very important" compared to higher percentages in other fields like Economics (51.7%), Political Science (48.1%), and Psychology (43.8%). Sociologists report a lower percentage of strong supporters (29.4%) than the accounting researchers in our sample, suggesting varied attitudes towards open science across the disciplines.

@@

>>>>

---
editor: source
title: |
  | How Does the Accounting Research Community
  | Think About Open Science?^[Joachim Gassen is based at Humboldt-Universität zu Berlin, while Jacqueline Klug and Victor van Pelt are affiliated with WHU - Otto Beisheim School of Management. We thank Kris Hardies, Stephan Hollander, and Maximilian Müller, as well as audiences at University of Antwerp, BI Norwegian Business School, Humboldt University Berlin, Stanford University, the TRR 266 Annual Conference, and WHU for providing helpful feedback. Scott Summers and David Wood thankfully provided data from the BYU Accounting Research Rankings. Excellent research assistance by Benedikt Hahn, Fabian Kalife, and Timnah Weckner is gratefully acknowledged. This study was approved by the WHU Ethical Review Board and supported by Deutsche Forschungsgemeinschaft (Project-ID 403041268, TRR 266 Accounting for Transparency).]
author: 
  - name: Joachim Gassen
    email: gassen@wiwi.hu-berlin.de
    affiliation: Humboldt-Universität zu Berlin
  - name: Jacqueline Klug
    email: Jacqueline.Klug@whu.edu
    affiliation: WHU Otto Beisheim School of Management
  - name: Victor van Pelt
    email: Victor.vanPelt@whu.edu 
    affiliation: WHU Otto Beisheim School of Management
date: last-modified
date-format: long
execute:
  echo: false
  message: false
  warning: false
format:
  pdf:
    documentclass: article
    template-partials:
      - materials/title.tex
    number-sections: true
    colorlinks: true
    papersize: letter
    fig-pos: H
    fig_caption: yes
    fig-cap-location: top
    geometry: margin=1in
    fontsize: 11pt
    ident: yes
ourabstract: We explore the attitudes of the accounting research community towards open science practices by surveying a sample of scholars who have published in leading accounting journals. Building on a discussion of the costs and benefits of open accounting research, we find that accounting researchers, compared to peers from other social science disciplines, are more skeptical about the reproducibility of their influential findings. Additionally, they state to be less familiar with publicly sharing research materials and to pre-register their study designs less frequently. Despite believing that both the accounting research community and journal editors support the sharing of research materials, there is skepticism regarding its actual prevalence. To supplement these survey insights, we analyze observational data, revealing that research material sharing is relatively uncommon and predominantly associated with journals enforcing data and code sharing policies. Finally, our data suggests that accounting researchers view research material sharing as yielding low private benefits but high private costs. We interpret our evidence as indicative of an "accounting open science dilemma" and propose strategies for effectively addressing this issue.

@@

sr <- readRDS("../data/generated/survey_response.rds")
mr <- readRDS("../data/generated/merged_response.rds")
vr <- readRDS("../data/generated/verbal_response_coded.rds")

vars <- read_csv("../data/external/variables.csv", show_col_types = FALSE)
pop <- read_csv("../data/external/invited_authors_anon.csv", show_col_types = FALSE)
byu <- read_csv("../data/external/byu_author_data_anon.csv", show_col_types = FALSE)

@@

sr$exp_tment_collab <- 1 - sr$exp_tment_control
svr <-sr %>% left_join(vr %>% select(-exp_reflect), by = "id")

modh1 <- lm(exp_pct_share ~ exp_tment_collab, data = sr)
modh2 <- lm(exp_pct_share ~ exp_tment_private, data = sr)
modh3 <- lm(exp_pct_share ~ exp_tment_collab*exp_tment_private, data = sr)

@@

gt_add_header_mpage_table <- function(x) {
  x <- sub("\\\\midrule", "\\\\midrule \\\\endhead", x)
  x
}
```

::: {.content-visible when-meta="paper-titlepage"}

```{=tex}
\thispagestyle{empty}
\begin{abstract}
\singlespace
```

{{< meta ourabstract >}}

```{=tex}
\end{abstract}
\vspace{0.5cm}
\begin{flushleft}
\textbf{Keywords}: Accounting Research, Open Science, Reproducibility, Research Material Sharing, Pre-Registration, Survey \newline
\textbf{Data Availability}: Data available in code repository \newline
\textbf{Code Repository}: \href{https://github.com/joachim-gassen/osacc}{https://github.com/joachim-gassen/osacc}  \newline
\textbf{Survey Dashboard}: \href{https://jgassen.shinyapps.io/osacc/}{https://jgassen.shinyapps.io/osacc} \newline
\textbf{Declaration of Interest}: The author(s) declare(s) that they have no conflict of interest \newline
\end{flushleft}
```

:::

::: {.content-visible when-meta="paper-body"}

```{=tex}
\pagebreak
\setcounter{page}{1}
```

::: {.content-visible when-meta="anonymize"}

```{=tex}
\begin{center}
\Large
\textbf{How Does the Accounting Research Community\\Think About Open Science?}
\normalsize
\end{center}
\begin{abstract}
\singlespace
```

{{< meta ourabstract >}}

```{=tex}
\end{abstract}
\vspace{0.5cm}
```

:::

@@

Cumulative research relies on reproducibility, which refers to the ability to recreate the results of previous studies using the same materials as the original researchers [@NSF_2015].[^1] Across all fields of science [@B_2016; @CDF_2016; @M_2017] and within accounting [@HLL_2020; @G_2023; @S_2023; @CGL_2024], scholars have diagnosed shortcomings in reproducibility and advocated the use of various open science methods. Open science implies conducting research in ways that allow others to collaborate and contribute. Two key open science methods proposed to enhance the reproducibility of research include the public sharing of research materials and the pre-registration of study plans. In recent years, there has been a noticeable increase in the adoption of these open science methods in social sciences [@FLCPSWMBP_2023].

[^1]: The terms "reproduction" and "replication" are at times used as synonyms but have different meanings. Reproduction refers to achieving the same results of a prior study using the same materials (code, procedures, and data), while replication refers to duplicating the results of a of a prior study using the same code and procedures but new data [@NSF_2015; @BCKU_2024]. For a more in-depth discussion of the differences and related terminological debate, see @DJ_2024.

The sharing of research materials and the use of pre-registrations can be understood as disclosure mechanisms that enable researchers to contribute public goods to the academic community while also signaling the quality of their work. Despite their potential benefits, researchers may rationally under-engage in these activities due to limited private benefits and substantial direct and indirect costs. This could lead to a socially sub-optimal provision of public research materials causing a general lack of research transparency. Starting from this conceptual framework, we conduct a survey among accounting researchers to explore their perceptions and attitudes towards open science.

Based on the responses of `r nrow(sr)` published accounting researchers, our findings reveal that the accounting community's attitudes towards open science clearly differ from the views of other social scientists. Notably, accounting researchers exhibit a generally more pessimistic perspective on the reproducibility of their domain's influential work. In contrast to economists and sociologists, for instance, accounting researchers are approximately half a point more skeptical on a 5-point Likert scale. Both analytical and qualitative researchers demonstrate heightened levels of skepticism. Analytical researchers are particularly critical of research employing non-analytical methods. This indicates that methodological differences might influence perceptions of research reproducibility within the field of accounting.

Given these findings, it could be expected that accounting researchers would adopt a proactive stance and embrace open science practices to enhance research reproducibility. However, our data reveal that, compared to their counterparts in other social science disciplines, accounting researchers state to be less familiar with the practice of publicly sharing research materials and assign it less importance. Respondents using archival, field, and experimental methods demonstrate the highest familiarity with this practice. Conversely, those employing qualitative methods report both the least familiarity and a diminished perception of its significance. This suggests that methodological orientation may influence attitudes toward the adoption of open science practices within the field of accounting.

Similar to, albeit even more pronounced than, other social science researchers, accounting researchers exhibit a disparity between their perceived importance of sharing research materials (prescriptive), their willingness to do so (stated), and their perception of actual sharing practices within their community (descriptive). While 57% of respondents report that they at least sometimes share their research materials publicly, only about 44% believe that this practice is favored among their peers. Interestingly, they estimate that 61% of top-six accounting journal editors support material sharing. This might suggest a generally supportive stance within the community. However, the view of the reality is more sobering: when asked about actual sharing behavior, our respondents estimate on average that only 27% of accounting researchers actually publicly share research materials. These perceptions vary significantly across methodological areas too. Analytical researchers demonstrate the narrowest gap, expecting 43% of accounting researchers to be in favor of sharing, while estimating that 38% actually do so. In contrast, archival researchers report the widest gap, with 45% expected to support sharing but only 24% expected to engage in it. Qualitative researchers report the lowest figures overall, with just 36% perceiving support for sharing and estimating that only 18% engage in the practice. This variability underscores a significant disparity between the perceived and actual sharing of research materials in accounting academia, particularly across different methodological approaches.

In terms of pre-registration, accounting researchers exhibit a familiarity with the concept similar to that of their peers in other social sciences. Despite this, they report adopting pre-registration practices approximately two years later than their counterparts and using it less often, with only 17% practicing pre-registration compared to 27% in other fields. While their trust in pre-registered work aligns with that of other social science researchers, it notably falls short of the high trust levels seen in Psychology, where pre-registration is most prevalent.

To contrast these perceptions with actual behavior, we collected additional observational data from a country-stratified random sample of `r nrow(authors)` authors within our target population. Our findings indicate that 39% of these authors engage in some form of research material sharing, significantly lower than the 57% of our respondents claiming that they at least sometimes share research data but higher than the skeptical mean of 27% that they estimate for the actual sharing rate. A deeper analysis of the observational data reveals that in accounting, material sharing often appears as an occasional compliance measure. Specifically, only 7.5% of the papers authored by individuals in this dataset are published with accessible research materials. Also, when we exclude Journal of Accounting Research and Management Science, two journals with data and code sharing policies, the share of authors for which we document at least some form of research material sharing drops from 39% to 23%. Furthermore, we document relatively few pre-registrations in our observational data, and all are linked to the Registered Report Initiative of the Journal of Accounting Research.

In light of these findings, a logical next step is to investigate the primary rationales for and against sharing research materials. We approach this through a brief experimental design involving a hypothetical scenario.[^2] In the scenario, accounting researchers were asked how likely they would be to share their research materials with a fellow researcher upon request. They reported an average likelihood of 72%. The probability of sharing was unaffected by the randomized rationale provided (i.e., whether the fellow researcher expressed an intent to collaborate or control) or the decision's scope (i.e., whether the fellow researcher requested to share the research materials publicly versus privately). Their reflections reveal that research material sharing in the hypothetical scenario is driven by a belief that it enhances both the quality of respondents' research and of research in general. Additionally, there is a desire to support fellow researchers. The most frequently cited reasons for not sharing include the proprietary nature of the data (noted by 56% of respondents), the time required to make materials available (30% of respondents), and the fear of being scooped once materials are public (23% of the respondents). The reasons given for withholding research materials in the hypothetical scenario vary across research methodologies. For qualitative researchers, issues with deidentification are notably prominent (46%). Meanwhile, analytical researchers view the time investment needed to prepare materials as less of a deterrent compared to other researchers (only 9.5% versus 30% overall).

[^2]: We pre-registered this experimental part of our study at the [Open Science Foundation (link omitted for review)]{.content-visible when-meta="anonymize"}[[Open Science Foundation](https://osf.io/frmzt/)]{.content-visible unless-meta="anonymize"}.

Collectively, our findings indicate an "accounting open science dilemma": while accounting researchers express skepticism about the reproducibility of their research, they also question the efficacy of open science methods, such as research material sharing and pre-registration, in improving it. This dual skepticism may explain why these open science methods are currently less established in the accounting domain than in other fields. The assessments vary across methodological paradigms. Qualitative research faces challenges different from archival work, and they both differ again from experimental studies. In the concluding section of our paper, we discuss these challenges and offer recommendations to how the diagnosed dilemma might be overcome.

Our study contributes to the ongoing debate on reproducibility and transparency of accounting research. By building on the survey evidence presented by @HLL_2020, we provide more comprehensive and timely insights into accounting researchers' views regarding the reproducibility of their influential work, as well as the perceived advantages and disadvantages of open science practices. Furthermore, our study benchmarks these findings against those from related disciplines within the social sciences, facilitating a rough comparative analysis of how accounting researchers' perceptions align or differ from their peers in economics, psychology, sociology, and political science. Additionally, we corroborate recent evidence concerning the robustness of empirical work in accounting [@G_2023; @S_2023; @LSA_2024; @CGL_2024] and management science [@FGHKO_2023] by delving deeper into potential reasons why the discipline of accounting may, or may not, face issues with reproducibility.

@@

Many of the arguments that have been crafted around the costs and benefits of open science in general [@MS_2019; @AM_2019; @ABC_2021; @G_2022; @FLCPSWMBP_2023; @BCKU_2024] also apply to the field of accounting. Below, we present and extend some of these thoughts in a voluntary disclosure-inspired framework [@LT_2005; @MS_2019; @BCLW_2010]. For this purpose, our discussion will be primarily anchored on research material sharing (the main focus of our study) but should largely extend to pre-registration as well. Understood as a disclosure activity related to underlying research, publicly available research materials constitute a public good. To the extent that they are reusable, they accelerate scientific discoveries, improving the quantity and, most likely, also the quality of research. Even if they are not reusable, they still reduce the costs of reproducing the original work, thereby reducing assurance costs. In analogy to classic auditing research [e.g., @S_1980]: reduced assurance costs should lead to an overall increase in assurance activities, ultimately resulting in better research quality.

This means that, similar to other disclosure activities, sharing research materials does not necessarily benefit the producer but the research community at large. While intrinsic motivation for good research can be expected to be a strong determinant of individuals self-selecting into the academic accounting profession, one can still expect accounting researchers to under-engage in research material sharing because the production costs are mostly private while the benefits are mostly public. So, are there any private benefits to sharing research materials? Besides the warm glow of helping others, research material sharing likely improves the quality of the sharing individual's research output. First, it increases the likelihood that mistakes, if present, are being detected. As such incidents likely impose a cost on sharing researchers, this should increase research care prior to sharing. Second and related, if research materials are shared relatively early, the sharing researcher can directly benefit from community feedback prior to the ultimate publication of the study. Uncovered mistakes can also be an important learning opportunity, improving research quality in the long run.

Based on these arguments, there are reasons to believe that voluntary research material sharing can act as a signal for research quality, creating an incentive for researchers to use it to signal the quality of their work in the publishing and career process. In ideal circumstances, we should obtain the well-known unraveling result where researchers even share and improve low-quality research because the research community would otherwise assume the worst [@M_1981]. One critical obstacle to the unraveling result are disclosure costs [@V_1983], also known as proprietary costs in the disclosure literature. For research materials sharing to unravel, it is important that the costs of sharing are sufficiently low, especially for researchers that produce high-quality work.

The direct costs of research material sharing can be sizable as preparing data, code and research procedures for dissemination requires care, and care requires time. While care will also improve quality (see above), at least some of the documentation and code refactoring work to increase accessibility and reusability will not directly pay off on the quality of the underlying work. Another important factor to consider is the cost of maintaining publicly available materials. While some replication packages or similar materials are static in nature and require only limited maintenance, most data and code packages require ongoing updating and support activities. One important aspect of maintenance costs is that they increase significantly with public demand. As demand is directly linked to the scientific impact of the underlying work, high maintenance cost sharing activities are likely to also be high parivate and public benefit activities.

The indirect costs of research material sharing are, first and foremost, linked to the quality assurance process outlined above. Flaws in publicly shared research materials can trigger behavioral (shame and regret) and reputation costs. Specifically, accounting researchers may implicitly assume that reproduction failures could lead others to suspect questionable research practices. However, this suspicion might be unwarranted, as failed reproductions can result from honest mistakes. Another important aspect are proprietary costs from scientific competition. While likely to be positive from the societal perspective, the indirect individual costs of being "scooped" for an interesting follow-up project can be sizable. Finally, there is also the possibility of unethical misuse of shared research materials. Malevolent researchers might use shared materials without proper attribution or use it with a strategy of "reverse p-hacking", meaning creating reproductions or replications that communicate a biased picture of the overall evidence to increase their chances for publication.

In this simplified disclosure framework, rational researchers can be expected to voluntarily share research materials when their private benefits outweigh their private costs. Whether this happens will critically depend on whether the signaling mechanism outlined above unfolds. In a credence good market like research, signaling is a key mechanism to avoid market failure. Based on the discussion above, a critical aspect could be the proprietary cost of competition, as one could argue that this cost is higher for high quality researchers with innovative ideas than for low-quality researchers who will likely face limited demand for their materials. Also, the risks of reputation costs or misuse of materials could be higher for high-quality researchers. On the other hand, it can be argued that direct costs should be lower for high-quality researchers because of superior skills. Finally, outside options should be generally higher for high-quality researchers, meaning that they face higher opportunity costs of their time but also less competitive pressure to keep their research materials private.

The discussion should sound familiar to those who study voluntary disclosures by firms. What is different from our traditional firm-setting is that most researchers are not acting as entrepreneurs. Instead, they are employed by academic institutions or act as civil servants. This can, to some extent, mute the relevance of the benefits and the costs outlined above, at least for researchers with tenured positions. In addition, the employing institutions might also interact with the decision of whether or not to make research materials available. They are designing performance and tenure evaluation criteria that incentivize researchers. Also, they compensate researchers for their time and they provide them with infrastructure that influences and, at times, drastically reduces the direct costs of research material sharing. They might even hold property rights on the intellectual capital that their employees generate. Based on the public announcements of many leading academic institutions, it seems as if these are generally advocating the positive externalities of research material sharing. However, the incentive systems designed by these institutions appear at least in parts inconsistent with these announcements, as they value individual research achievements in form of publications and only rarely publicly available research materials.

Finally, publishers and journals are influential in research material sharing decisions as well. Leading journals have established rigorous data and code sharing guidelines, essentially transforming the voluntary disclosure decision into a mandatory disclosure requirement. While it is interesting to question how journal competition affects the dissemination of data and code sharing guidelines, it seems as if imposing mandatory disclosure rules is a classic response to overcome the diagnosed public good problem.

@@

The first two questions are descriptive in nature. We compare the response of our sample with responses by researchers from other social science fields. While the first question sets the stage by assessing whether our participants sense accounting research to face a reproducibility crisis, the second question explores whether accounting researchers believe that research material sharing and pre-registration are viable strategies and sufficiently common to increase the reproducibility of research. Here too, comparing the views of accounting academics with the views of neighboring fields is essential for a comprehensive understanding of these practices within the wider academic community.

The third question strives to understand the potential causes behind these assessments. Using a small experimental component within our survey, we ask respondents how likely they would be to share their research materials with a fellow researcher. We examine whether respondents' sharing likelihood depends on two aspects of a hypothetical sharing request by a fellow researcher, namely, its rationale (i.e., whether the fellow researcher expressed an intent to collaborate or control) and its scope (i.e., whether the fellow researcher requests to share the research materials publicly versus privately). Our motivation for the treatments is that the rationale should shift the focus from benefits (collaboration) to costs (control) while the scope treatment should manipulate the salience of indirect costs. Besides studying the effect of these two experimental treatments, we also use structured and unstructured survey response data to uncover perceived benefits and costs from research material sharing.

@@

Figure 4 provides a graphical representation of these findings, depicting frequencies along horizontal axes and aligning them to a neutral midpoint. In our study, only 39.6% of accounting researchers consider research material sharing "very important." This is notably lower than the percentages observed in other fields: Economics at 51.7%, Political Science at 48.1%, and Psychology at 43.8%. Sociologists report an even lower percentage of strong advocates, at 29.4%, compared to accounting researchers. These variations indicate differing attitudes towards open science across academic disciplines.

@@

:::
